Predicting Success of Clinical Interviews via Probabilistic Modeling of Patient-Provider Communication Sequences

### 2017-03-10 paper/AMIA/main.tex
Modified the authors order and their contribution

\documentclass{amia}
\usepackage{graphicx}
\usepackage[labelfont=bf]{caption}
\usepackage[superscript,nomove]{cite}
\usepackage{color}
\usepackage{multirow}

@@

\author{Mehedi Hasan, BS$^{1}$, Alexander Kotov, PhD$^{1}$, April Idalski Carcone, PhD$^{2}$, Ming Dong, PhD$^{1}$, Sylvie Naar, PhD$^{2}$}

>>>>

\documentclass{amia}
\usepackage{graphicx}
\usepackage[labelfont=bf]{caption}
\usepackage[superscript,nomove]{cite}
\usepackage{color}
\usepackage{multirow}
\renewcommand*{\thefootnote}{\fnsymbol{footnote}}

@@

\author{Alexander Kotov, PhD$^{1}$\footnote[1]{Authors provided equal contribution. \label{footnote1}}, Mehedi Hasan, BS$^{1}$\textsuperscript{\ref{footnote1}}, April Idalski Carcone, PhD$^{2}$, Ming Dong, PhD$^{1}$, Sylvie Naar, PhD$^{2}$}
